ExpressionView

### 2011-10-18 RExpressionView/inst/doc/ExpressionView.tutorial.Rnw
EV updates from SVN, version number increased.

The \Rfunction{OrderEV} function implemented in the
\Rpackage{ExpressionView} package determines the optimal order of the
gene expression matrix for a given set of biclusters. It can be called
with \Rclass{ISAModules} or \Rclass{Biclust} objects as the first argument:
<<expressionview, results=HIDE>>=
library(ExpressionView)
optimalorder <- OrderEV(modules)
@

>>>>

The \Rfunction{OrderEV} function implemented in the
\Rpackage{ExpressionView} package determines the optimal order of the
gene expression matrix for a given set of biclusters. It can be called
with \Rclass{ISAModules} or \Rclass{Biclust} objects as the first argument:
<<expressionview, results=hide>>=
library(ExpressionView)
optimalorder <- OrderEV(modules)
@
